Network segregation and Preferences for Redistribution across societies

### 2023-10-19 paper.Rmd
plotcoef

m1_df <-
    broom.mixed::tidy(rob1) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
                                                    "class3Working Class (V+VI+VII)",
                                                    "homclass"))

@@

     relabel_predictors(
        c("homclass"="Class based network homogeneity",
          "class3Intermediate class (III+IV)"="Intermediate Class (ref: Service class)",
          "class3Working Class (V+VI+VII)"="Working Class",
          "class3Intermediate class (III+IV):homclass"="Homogeneity x Intermediate Class",
          "class3Working Class (V+VI+VII):homclass"="Homogeneity x Working Class"))+
      ggtitle("Multilevel regression for Network segregation, social class and redistributive preferences") +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  theme(
        plot.title = element_text(face = "bold"),
        # legend.position = c(0.007, 0.01),
        # legend.justification = c(0, 0),
        # legend.background = element_rect(colour = "grey80"),
        # legend.title = element_blank(),
        axis.text.y.left = element_text(face = "bold",size = 12)
  )
```

>>>>

m1_df <-
    broom.mixed::tidy(rob1,conf.int = TRUE) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
                                                    "class3Working Class (V+VI+VII)",
                                                    "homclass"))

@@

     relabel_predictors(
        c("homclass"="Class based network homogeneity",
          "class3Intermediate class (III+IV)"="Intermediate Class (ref: Service class)",
          "class3Working Class (V+VI+VII)"="Working Class",
          "class3Intermediate class (III+IV):homclass"="Homogeneity x Intermediate Class",
          "class3Working Class (V+VI+VII):homclass"="Homogeneity x Working Class"))+
      ggtitle("Multilevel regression for Network segregation, social class and redistributive preferences") +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  theme(
        plot.title = element_text(face = "bold"),
        # legend.position = c(0.007, 0.01),
        # legend.justification = c(0, 0),
        # legend.background = element_rect(colour = "grey80"),
        # legend.title = element_blank(),
        axis.text.y.left = element_text(face = "bold",size = 12)
  )

ggplot(
  m1_df,
  aes(x = estimate, y = term, colour=term)) +
  geom_vline(xintercept = 0) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_x_continuous(labels = label_percent()) +
  guides(color = "none") +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  theme(
        axis.text.y.left = element_text(face = "bold",size = 12)
  )

```
